\addchap*{Abstract}
\label{abstract}
{\LARGE Visualization Verification of Complex Avionic Models Using Computer Vision}

With the growing complexity of applications in aviation, the use of \acrlong{dsm} (\acrshort{dsm}) in the field has become vital. It enables engineers to work on larger and more complex applications more efficiently and, through automatic code generation, significantly reduces the number of errors in the resulting programs. For use in safety-critical applications however, \acrshort{dsm} requires significant verification effort. One important aspect of \acrshort{dsm} in these applications is ensuring a correct model visualization to increase safety and reduce the amount of manual verification work.\\
This thesis aims to improve the reliability of the automated verification of block-diagram visualizations in \acrshort{dsm}. Computer vision techniques are used to recognize and process block diagram models. The recognized data is compared with the original model to find and indicate deviations to the user inside a browser-based graphical model editor.\\
This thesis extends the capabilities of the block diagram recognition algorithm to work with complex and diverse diagrams in three graphical \acrlong{dsl}s (\acrshort{dsl}s). The new implementation is able to correctly identify and process intersecting or partially obscured lines in any orientation, detect a larger variety of vertices, and process text labels in multiple orientations, showcasing its potential to significantly reduce manual verification effort in \acrshort{dsm} applications.\\
The new implementation is evaluated using a set of 20 unique test cases, each containing one or two block diagrams with a single simulated error. The results show that the implementation is able to correctly identify and textually indicate all simulated errors to the user, differentiating between different error types. If possible, the implementation visually provides the position of the found errors inside the model editor alongside the textual indication.